\documentclass[11pt,a4paper]{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage[top=6.00mm, bottom=0.00cm]{geometry}
\author{Rathin Dholakia}
\title{List of Papers}
\begin{document}
\begin{enumerate}
\item A.G. Phadke and J. S. Thorp, `` HISTORY AND APPLICATIONS OF PHASOR MEASUREMENTS", 2006 IEEE PES Power Systems Conference and Exposition, Atlanta, GA, 2006, pp. 331-335.
\item A. G. Phadke,M. G. Adamiak, ``A NEW MEASUREMENT TECHNIQUE FOR TRACKING VOLTAGE PHASOR, FREQUENCY, AND RATE OF CHANGE OF FREQUENCY, IEEE PES, 1982.
\item  C37.118 - IEEE Standard for Synchrophasor Measurements for Power Systems
\item Phadke, A.G., Thorp, J.S.,  \textit{Synchronized Phasor Measurements and Their Applications}, Springer US, 2008.
\item Saugata S. Biswas, Jeong Hun Kim, Anurag K Srivastava ``Development of a Smart Grid Test Bed and Applications in PMU and PDC Testing", \textit{IEEE Conference Publications}, 2012.
\item R. Ghiga, Q. Wu, K. Martin, W. Z. El-Khatib, L. Cheng and A. H. Nielsen ``Dynamic PMU Compliance Test under C37.118.1aTM-2014", \textit{IEEE PES GM}, PAge 1-5, 2015
\item Krish Narendra, Dinesh Rangana Gurusinghe, \textit{Dynamic Performance Evaluation and Testing of Phasor Measurement Unit (PMU) as per IEEE C37.118.1 Standard}, Doble Client Commitee, 2012 
\item J. Depablos, V. Centeno, A. G. Phadke and M. Ingram, "Comparative testing of synchronized phasor measurement units," Power Engineering Society General Meeting, 2004. IEEE, 2004, pp. 948-954 Vol.1.
\item J. Kilter, I. Palu, M. S. Almas and L. Vanfretti, "Experiences with dynamic PMU compliance testing using standard relay testing equipment," Innovative Smart Grid Technologies Conference (ISGT), 2015 IEEE Power \& Energy Society, Washington, DC, 2015, pp. 1-5.
\item T. Bi, Y. Zhang, X. Xiao, P. Forsyth and R. Wierckx, "Large scale power system simulation and PMU testing using a real time digital simulator," 2007 International Power Engineering Conference (IPEC 2007), Singapore, 2007, pp. 383-388.
\item Paolo Romano, Marco Pignati and Mario Paolone, ``Integration of an IEEE Std. C37.118 Compliant PMU into a Real-Time Simulator"
\end{enumerate}
\end{document}